---
title: "Class Exercise 1"
author: "Sergei Korotkikh, Vadim Maletskii"
date: "27/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Relationship between people's trust in police and their feeling safe alone outside at night

## Introduction

People usually do not feel being alone outside at night. However, if they know that the police can save them from burglars or killers, they are less stressed about it.

## Methods

We have used the ESS10 dataset and took the variables __trstplc__ (Trust in the police) and __aesfdrk__ (Feeling of safety of walking alone in local area after dark). The first variable ranges from 0 (No trust at all) to 10 (Complete trust), whereas the second variable ranges from 1 (Very safe) to 4 (Very unsafe).

In our opinion, **the more people trust the police, the safer they feel walking alone in local area after dark.**

## Data preparation

Loading the __tidyverse__ package:

```{r, eval = F}
library(tidyverse)
```

We needed to remove the NAs and extract the two variables necessary for the research:

```{r, eval = F}
# Importing the data and removing the NAs ----
ess <- rio::import('Data_orig/ESS10.dta')
ess[ess == '77'] <- NA
ess[ess == '88'] <- NA
ess[ess == '99'] <- NA

# Selecting the variables needed and removing the NAs ----
pol_safe <- ess %>% select(trstplc, aesfdrk)
pol_safe <- na.omit(pol_safe)
pol_safe <- pol_safe %>% mutate(aesfdrk = replace(aesfdrk, aesfdrk %in% c(7, 8, 9), NA))
pol_safe <- na.omit(pol_safe)

# Creating the CSV file with the new data ----
rio::export(pol_safe, here::here("Data_preproc", 'pol_safe.csv'))
```

## Calculating the means

Next, we needed to see the means of the variable __aesfdrk__ for each value of the __trstplc__ variable:

```{r, eval = F}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
